### 2020-02-11 ChapterResults/chapterResults.tex
Fixed: Wording for ratio graph captions

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a latency tolerance of $2ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a latency tolerance of $8ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a latency tolerance of $16ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyHigh}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $8ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs.frame-time using a frame-time tolerance of $15ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs.frame-time using a frame-time tolerance of $25ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeHigh}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Latency using a latency tolerance of $2ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Latency using a latency tolerance of $8ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Latency using a latency tolerance of $16ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyHigh}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $8ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $15ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $25ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeHigh}
\end{figure}
